Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-05-17 paper/manuscript.tex
Revise membrane paragraph based on Irfan feedback

\paragraph{Membrane proteins require additional care}
Integral membrane proteins require embedding in a suitable model membrane to remain stable during simulations. Lipids are often not included in protein force fields and, although they may be covered by generic small molecule force fields, have often been parameterized separately (e.g., AMBER's Lipid21 \cite{AMBERLipid21}, CHARMM lipid force field \cite{CHARMMLipidFF}, and OpenFF's upcoming (?) ``biopolymer" force field). Membrane systems can be simulated in multiple thermodynamic ensembles, but the semi-isotropic scheme $NP_{z}P_{xy}T$ is frequently employed, allowing the pressure in the bilayer plane ($xy$) to scale independently \cite{LipidBestPracticesCOMS}. These systems require more extensive equilibration than soluble proteins. Some packages, such as Desmond, include a 7-step protocol to relax membrane systems.

In the case of a lipid-facing binding site, there are two additional challenges. First, simulation time should be extended to ensure sufficient sampling of lipid configurational space. Second, the free energy of binding for a small molecule may be strongly coupled to the lipid species. In some cases, the identity of the lipid may be known. But in other cases, it may be difficult to discern the identity of the lipid from X-ray or CryoEM structures due to the flexible nature of lipid head groups and benchmarking is recommended to match experimental data.

>>>>

\paragraph{Membrane proteins require additional care}
Integral membrane proteins require embedding in a suitable model membrane to remain stable during simulations. Lipids are usually not included in protein force fields and, although they may be covered by generic small molecule force fields, have often been parameterized separately (e.g., AMBER's Lipid21 \cite{AMBERLipid21} and the CHARMM lipid force field \cite{CHARMMLipidFF}). Membrane systems can be simulated in multiple thermodynamic ensembles, but the semi-isotropic scheme $NP_{z}P_{xy}T$ is frequently employed, allowing the pressure in the bilayer plane ($xy$) to scale independently \cite{LipidBestPracticesCOMS}. These systems require more extensive equilibration than soluble proteins. Some packages, such as Desmond, include a 7-step protocol to relax membrane systems.

Alchemical transformations that involve net charge changes can provide difficulties for membrane systems; phospholipids carry functional groups with nonzero formal charge and cannot be treated as a solvent with a uniform dielectric in the same way as water. Several approaches are reviewed in \cite{wu2022correction-51c} and the recommended method is to use a co-alchemical ion to maintain system neutrality.

In the case of a lipid-facing binding site, there are two additional challenges. First, simulation time should be extended to ensure sufficient sampling of lipid configurational space. Lipids may either bind alongside small molecules, acting as cofactors, or be displaced from the binding site by a ligand. If lipids participate in binding through protein-lipid or ligand-lipid interactions, it is necessary to sample these intermolecular interactions through additional $\lambda$ windows, longer simulation times, or different alchemical protocols. Displacing a lipid will have its own free energy cost which may take a long time to converge if it requires diffusion and rearrangement of nearby lipids. Second, the free energy of binding for a small molecule may be strongly coupled to the lipid species. In some cases, the identity of the lipid may be known. But in other cases, it may be difficult to discern the identity of the lipid from X-ray or cryo-EM structures due to the flexible nature of lipid head groups and benchmarking is recommended to match experimental data.
